Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-28 paper/paper.tex
looking nicely

\usepackage{listings}
\usepackage[lighttt]{lmodern}
\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\lstdefinestyle{default}{language=Anglican, basicstyle=\ttfamily\small, showstringspaces=false}

@@

An execution of the query may result in the following
sequence of checkpoint invocations:
\begin{lstlisting}[style=default]
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C2 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C3 ...)
\end{lstlisting}
According to the addressing scheme, the addresses generated
for this invocations are
\begin{verbatim}
    [C1 0]
    [C2 0]
    [C2 1]
    [C1 16]
    [C1 17]
    [C1 18]
    [C2 16]
    [C3 0]
\end{verbatim}
If the program is run by a Metropolis-Hastings algorithm, then a small change usually takes place in the sequence of checkpoints with each invocation, and the new sequence may become
\begin{lstlisting}[style=default]
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C2 ...)
    (sample 'C3 ...)
\end{lstlisting}
The addresses for the new sequence are
\begin{verbatim}
    [C1 0]
    [C2 0]
    [C1 16]
    [C1 17]
    [C2 16]
    [C2 17]
    [C3 0]
\end{verbatim}
Despite the change, the correspondence between checkpoints of
similar types occurring in similar positions (relative positions
in contiguous subsequences of a certain type) is preserved, and
drawn values can be reused efficiently:

\vspace{\baselineskip}
\begin{tabular}{l l}
    \textbf{old} & \textbf{new} \\ \hline
    {}\texttt{[C1 0]} & \texttt{[C1 0]} \\
    {}\texttt{[C2 0]} & \texttt{[C2 0]} \\
    {}\texttt{[C2 1]} & \textit{unused} \\
    {}\texttt{[C1 16]} & \texttt{[C1 16]} \\
    {}\texttt{[C1 17]} & \texttt{[C1 17]} \\
    {}\texttt{[C1 18]} & \textit{unused} \\
    {}\texttt{[C2 16]} & \texttt{[C2 16]} \\
    \textit{missing} & \texttt{[C2 17]} \textit{drawn}\\
    {}\texttt{[C3 0]} & \texttt{[C3 0]}
\end{tabular}
\vspace{\baselineskip}

@@

\begin{verbatim}
{S28209
 {(0 anglican.runtime.normal-distribution)
  {:mean 10.99753360180663,
   :sd 0.7290976433082352}},
 S28217
 {(0 anglican.runtime.normal-distribution)
  {:mean 12.668050292254202,
   :sd 0.9446695174790353}},
 S28215
 {(0 anglican.runtime.normal-distribution)
  {:mean 9.104132559955836,
   :sd 0.9479290526821788}},
 S28219
 {(0 anglican.runtime.flip-distribution)
  {:p 0.11671977016875924,
   :dist
   {:min 0.0,
    :max 1.0}}}}
\end{verbatim}

@@

\begin{verbatim}
{:arrivate-time-same
 {(0 anglican.runtime.normal-distribution)
  {:mean 10.99753360180663,
   :sd 0.7290976433082352}},
 :arrival-time-first
 {(0 anglican.runtime.normal-distribution)
  {:mean 12.668050292254202,
   :sd 0.9446695174790353}},
 :arrival-time-second
 {(0 anglican.runtime.normal-distribution)
  {:mean 9.104132559955836,
   :sd 0.9479290526821788}},
 :same-or-different
 {(0 anglican.runtime.flip-distribution)
  {:p 0.11671977016875924,
   :dist
   {:min 0.0,
    :max 1.0}}}}
\end{verbatim}

>>>>

\usepackage{listings}
\usepackage{lmodern}
\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
\lstdefinestyle{default}{language=Anglican, basicstyle=\ttfamily\small, columns=flexible, showstringspaces=false}

@@

An execution of the query may result in the following
sequence of checkpoint invocations:
\begin{lstlisting}[style=default]
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C2 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C3 ...)
\end{lstlisting}
According to the addressing scheme, the addresses generated
for this invocations are
\begin{lstlisting}[style=default]
    [C1 0]
    [C2 0]
    [C2 1]
    [C1 16]
    [C1 17]
    [C1 18]
    [C2 16]
    [C3 0]
\end{lstlisting}
If the program is run by a Metropolis-Hastings algorithm, then a small change usually takes place in the sequence of checkpoints with each invocation, and the new sequence may become
\begin{lstlisting}[style=default]
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C1 ...)
    (sample 'C1 ...)
    (sample 'C2 ...)
    (sample 'C2 ...)
    (sample 'C3 ...)
\end{lstlisting}
The addresses for the new sequence are
\begin{lstlisting}[style=default]
    [C1 0]
    [C2 0]
    [C1 16]
    [C1 17]
    [C2 16]
    [C2 17]
    [C3 0]
\end{lstlisting}
Despite the change, the correspondence between checkpoints of
similar types occurring in similar positions (relative positions
in contiguous subsequences of a certain type) is preserved, and
drawn values can be reused efficiently:

\vspace{\baselineskip}
{\small
\begin{tabular}{l l}
    \textbf{old} & \textbf{new} \\ \hline
    {}\texttt{[C1 0]} & \texttt{[C1 0]} \\
    {}\texttt{[C2 0]} & \texttt{[C2 0]} \\
    {}\texttt{[C2 1]} & \textit{unused} \\
    {}\texttt{[C1 16]} & \texttt{[C1 16]} \\
    {}\texttt{[C1 17]} & \texttt{[C1 17]} \\
    {}\texttt{[C1 18]} & \textit{unused} \\
    {}\texttt{[C2 16]} & \texttt{[C2 16]} \\
    \textit{missing} & \texttt{[C2 17]} \textit{drawn}\\
    {}\texttt{[C3 0]} & \texttt{[C3 0]}
\end{tabular}
\vspace{\baselineskip}}

@@

\begin{lstlisting}[style=default]
{S28209
 {(0 anglican.runtime.normal-distribution)
  {:mean 10.99753360180663,
   :sd 0.7290976433082352}},
 S28217
 {(0 anglican.runtime.normal-distribution)
  {:mean 12.668050292254202,
   :sd 0.9446695174790353}},
 S28215
 {(0 anglican.runtime.normal-distribution)
  {:mean 9.104132559955836,
   :sd 0.9479290526821788}},
 S28219
 {(0 anglican.runtime.flip-distribution)
  {:p 0.11671977016875924,
   :dist
   {:min 0.0,
    :max 1.0}}}}
\end{lstlisting}

@@

\begin{lstlisting}[style=default]
{:arrivate-time-same
 {(0 anglican.runtime.normal-distribution)
  {:mean 10.99753360180663,
   :sd 0.7290976433082352}},
 :arrival-time-first
 {(0 anglican.runtime.normal-distribution)
  {:mean 12.668050292254202,
   :sd 0.9446695174790353}},
 :arrival-time-second
 {(0 anglican.runtime.normal-distribution)
  {:mean 9.104132559955836,
   :sd 0.9479290526821788}},
 :same-or-different
 {(0 anglican.runtime.flip-distribution)
  {:p 0.11671977016875924,
   :dist
   {:min 0.0,
    :max 1.0}}}}
\end{lstlisting}
